Instructions for ACL-IJCNLP 2021 Proceedings

### 2021-06-04 reports/SemDial2021/semdial.tex
intro cut-n-paste, another example

@@

\begin{figure}
  \includesvg[width=\linewidth]{img/box-swda}
  \caption{Box plot for proportions of dialogue act which contain laughs.}
  \label{fig:box-swda}
\end{figure}

Let us introduce our comparison schema for the other two outliers,
Downplayer and Apology, comparing them with the most common dialogue
act in SWDA---Statement-Non-Opinion.  We take into consideration five
laughter-related dimensions of an utterance, and create 5-dimensional
representations of dialogue acts according to them. Each dimension's
value equals to the proportion of utterances of a given type which
contain laughter.
\begin{itemize}
\item[$\uparrow$] current utterance;
\item[$\nwarrow$] previous utterance by the same speaker;
\item[$\swarrow$] previous utterance by the other speaker;
\item[$\nearrow$] next utterance by the same speaker;
\item[$\searrow$] next utterance by the other speaker.
\end{itemize}

\begin{figure}
  \includegraphics[width=\linewidth]{img/orbit-apology.pdf}
  \caption{Comparison of the most common dialogue act in
    SWDA---"Statement-Non-Opinion" (33.27\% of all utterances) with two
    outliers "Apology" (0.04\%) and "Downplayer" (0.05\%). Proportion
    of utterances which contain laughter are shown in association with
    each dialogue act. }
  \label{fig:orbit}
\end{figure}

% 1. overview: rather uniform distribution with few outliers
% 2. let's look at outliers
% 3. consider 5 dimensions of relations

For instance, 
\begin{lingex}
\item
  \adjustbox{valign=t}{
    \begin{tabulary}{\linewidth}{>{\bf}lJ>{\em}l}
    A: & I am so sorry to keep you on hold. & Apology \\
    B: & <Laughter> No problem. & Downplayer \\
    A: & Are you at work? & YN-Quest. \\
  \end{tabulary}}
\end{lingex}

>>>>

One important dialogical feature missing from text data is laughter,
which is ubiquitous in our everyday interactions.  We observe that in
the Switchboard dialogue corpus laughter comes about every 200 tokens.
Laughter also relates to the discourse structure of dialogue and can
relate to a \emph{laughable}, which can be an event or an entity in
the discourse (or external perceived event as well).  Laughter can
precede, follow or overlap the laughable, with the time alignment
between the laughter and laughable dependent on who produces the
laughable and the form of the laughter \citep{tian2016we}.  Laughter
can act as a contextual feature for determining the sincerity of an
utterance, e.g. when detecting sarcasm \citep{tepperman2006yeah}.

@@

\begin{figure}[htbp]
  \includesvg[width=\linewidth]{img/box-swda}
  \caption{Box plot for proportions of dialogue act which contain laughs.}
  \label{fig:box-swda}
\end{figure}

Let us introduce our comparison schema for the other two outliers,
Downplayer and Apology, comparing them with the most common dialogue
act in SWDA---Statement-Non-Opinion.  We take into consideration five
laughter-related dimensions of an utterance, and create 5-dimensional
representations of dialogue acts according to them. Each dimension's
value equals to the proportion of utterances of a given type which
contain laughter.
\begin{itemize}
\item[$\uparrow$] current utterance;
\item[$\nwarrow$] immediately preceding utterance by the same speaker;
\item[$\swarrow$] immediately preceding utterance by the other speaker;
\item[$\nearrow$] immediately following utterance by the same speaker;
\item[$\searrow$] immediately following utterance by the other speaker.
\end{itemize}

\begin{figure}[htbp]
  \includegraphics[width=\linewidth]{img/orbit-apology.pdf}
  \caption{Comparison of the most common dialogue act in
    SWDA---"Statement-Non-Opinion" (33.27\% of all utterances) with two
    outliers "Apology" (0.04\%) and "Downplayer" (0.05\%). Proportion
    of utterances which contain laughter are shown in association with
    each dialogue act. }
  \label{fig:orbit}
\end{figure}

For instance, \ref{ex:apology-downplayer} is an illustrative example
of the phenomenon shown on Figure \ref{fig:orbit}\footnote{Overlapping material is marked with hash signs.}. 
\begin{lingex}
\item\label{ex:apology-downplayer}
  \adjustbox{valign=t}{
    \begin{tabulary}{\linewidth}{>{\bf}lJ>{\em}R}
  A & I'm sorry to keep you waiting \#<laughter>.\# & Apology \\
  B & \#Okay\# <laughter>. / & Downplayer \\
  A & Uh, I was calling from work  & Statement (n/o) \\
    \end{tabulary}}
\end{lingex}
